\section{XSPICE}
\textit{Package comes with numerous pre-built models. These afford the simulation of digital and analog components that would be computationally-prohibitive if built atop only analog foundational components.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\href{https://sourceforge.net/p/ngspice/ngspice/ci/master/tree/src/xspice/icm/digital/}{Digital Models}}
{\footnotesize
\begin{multicols}{3}\noindent\begin{itemize}[label={},leftmargin=0pt,topsep=0pt]
    \item Buffer
    \item Inverter
    \item And
    \item Nand
    \item Or
    \item Nor
    \item Xor
    \item Xnor
    \item Tristate
    \item Pullup
    \item Pulldown
    \item D Flip Flop
    \item JK FF
    \item Toggle FF
    \item Set-Reset FF
    \item D Latch
    \item Set-Reset Latch
    \item State Mach\textquotesingle n
    \item Freq. Divid\textquotesingle r
    \item RAM
    \item Digital Source
    \item LUT
    \item General LUT
\end{itemize}\end{multicols}
}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\href{https://sourceforge.net/p/ngspice/ngspice/ci/master/tree/src/xspice/icm/analog/}{Analog Models}}
{\footnotesize
\begin{multicols}{3}\begin{itemize}[label={},leftmargin=0pt]
    \item Gain
    \item Summer
    \item Multiplier
    \item Divider
    \item Limiter
    \item Contrl\textquotesingle d Lmtr
    \item PWL Ctrl\textquotesingle d Src
    \item Filesource
    \item Analog Switch
    \item Zener Diode
    \item Current Limiter
    \item Hysteresis Blk
    \item Differentiator
    \item Integrator
    \item S-Domn Xfer F
    \item Slew-rate blk
    \item Induct. Coupl\textquotesingle g
    \item Magnetic Core
    \item Ctlrd Sine Osc
    \item Ctlrd Trng Osc 
    \item Ctlrd Sqr Osc
    \item Ctlrd 1-shot
    \item Cap\textquotesingle tance Mtr
    \item Inductance Mtr
    \item Memristor
    \item 2d table
    \item 3d table
    \item Simpl Diod Mdl
    \end{itemize}\end{multicols}
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Analog-Digital Bridge Models}
{\footnotesize
\begin{multicols}{2}\begin{itemize}[label={},leftmargin=0pt]
    \item D-to-A Node Bridge
    \item A-to-D Node Bridge
    \item Ctrld Digital Osc
    \item Node Bridge, D-to-Real
    \item Node Bridge, Real-to-A
    \item Gain Blk, Event Data
    \item Z**-1 Blk
\end{itemize}\end{multicols}
}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{User-Created}

\textit{For new models, create the \say{\ul{I}nterface \ul{S}pecification \ul{F}ile}, and \say{\ul{M}odel \ul{D}efinition \ul{F}ile}, the first which specifies the interface, the latter which implements it. For new \say{\ul{U}ser \ul{D}efined \ul{N}odes}, create a UDN file. The new files must be referenced via the }\texttt{ngspice/src/xspice/icm/<type>/modpath.lst}\textit{ file and then ngspice recompiled. ISFs comprise a table indicating metadata about the model\textquotesingle s \ul{ports}, \ul{parameters}, and \ul{storage variables}. MDFs implement the functionality ISFs specify in C code, making use of a number of \say{accessor macros} (circuit, parameter, and input and output data, etc), and helper functions (for data smoothing, simulator convergence control, $\mathbb{C}$-math, etc). Review \href{https://sourceforge.net/p/ngspice/ngspice/ci/master/tree/src/xspice/}{XSPICE sourcecode} to base new code off of other implementations.}\\


